An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: Write the section on the Peer

\subsection{The Peer}
% abstraction of what the peer is and does (sits below metadata/btsync, sits above system core)

>>>>

\subsection{The Peer}
% abstraction of what the peer is and does (sits below metadata/btsync, sits above system core)
In our implementation, we have a central object called the Peer. The Peer, as the name suggests, is used to represent the information and functionality associated with a single peer in the network. Much of the functionality of the controllers in the system core, which is described below, is implemented as calls to Peer methods. This is because the Peer is what allows access to the data and metadata layers. It also keeps track of the \textit{backed up files} part of the peer's metadata, in a data structure called the LocalBackupInfo. This information is important to all of the controllers in some way, helping to serve as their access to the peer's view of the relevant parts of the system.
